Non-convergence in iterative imputation

### 2025-10-21 Manuscript/manuscript.qmd
plot unique simulation repetitions

>>>>

```{r, eval=FALSE}
# plot each sim
performance |>
  filter(method == "MICE", mech == "MAR", term == "X3", prop == 0.5) |> 
  ggplot(aes(x = .it, y = psrf_mean, group = .sim)) +
  geom_hline(yintercept = 1, alpha = 0.1) + 
  geom_line(alpha = 0.1) +
  # geom_line(aes(y = psrf_mean_ll), linetype = "dashed", alpha = 0.3) +
  # geom_line(aes(y = psrf_mean_ul), linetype = "dashed", alpha = 0.3) +
  # facet_grid(term ~ mech + prop) +
  theme_classic()
```
